---
title: "Events"
description: ""
date: ""
toc: true
number-sections: false
format:
  html:
    page-layout: full
    code-fold: true
---

<style>
  /* Force hiding of the title */
  .pagelayout-title,
  .pagelayout-title h1,
  h1.pagetitle, /* Specific targeting for standalone titles */
  h1 {
    display: none !important;
    visibility: hidden !important;
    color: transparent !important;
  }
</style>


## <span style="color: #cc0000; font-weight: bold"> [**Events**]{.large}

<br>

### <span style="color: #2a71d0; font-weight: bold"> **Calendar**

<br>

```{r, include=FALSE}
library(shiny)
library(toastui)
library(bslib)
library(shiny)
library(shinyBS)
library(shinythemes)
library(shinydashboard)
library(shinyjs)
```

```{r, include=FALSE}
mycaldata=read.csv("assets/data/calender_bioEvents.csv", stringsAsFactors = F, fill=T, header=T)
#EVENT TITLE
mycaldata$title= ifelse(mycaldata$url != "", paste0("<a href='", mycaldata$url),mycaldata$url)
mycaldata$title= ifelse(mycaldata$url != "", paste0(mycaldata$title,"'>", mycaldata$course, "</a>"),mycaldata$url)
mycaldata$title= ifelse(mycaldata$url == "", mycaldata$course,mycaldata$title)
#EVENT BODY
mycaldata$Cost = paste0("Cost: ", mycaldata$Cost)
mycaldata$body = ifelse(mycaldata$registerlink != "", paste0("<a href='", mycaldata$registerlink),mycaldata$registerlink)
mycaldata$body= ifelse(mycaldata$registerlink != "", paste0(mycaldata$body,"'>", mycaldata$bodyText, "</a>"),mycaldata$registerlink)
mycaldata$body= paste0(mycaldata$body," ", mycaldata$Cost, " : ", mycaldata$Amount..if.not.free.)
mycaldata$body= gsub(" : +$","", mycaldata$body)
#EVENT TIME - All Day
mycaldata$start= ifelse(mycaldata$category=="allday",mycaldata$startDate,mycaldata$start)
mycaldata$end= ifelse(mycaldata$category=="allday", mycaldata$endDate,mycaldata$end)
#EVENT TIME - Time
mycaldata$start= ifelse(mycaldata$category=="time",paste0(mycaldata$startDate," ",mycaldata$startTime,":00"),mycaldata$start)
mycaldata$end= ifelse(mycaldata$category=="time", paste0(mycaldata$startDate," ",mycaldata$endTime,":00"),mycaldata$end)
#EVENT TIME - Time Series
#recurrenceRule=ifelse(mycaldata$startDate!=mycaldata$endDate, paste0(mycaldata$startDate," ",mycaldata$endTime),"")
#mycaldata = mycaldata[c("calendarId","title","body","recurrenceRule","start","end","category","location","backgroundColor","color","borderColor")]
#mycaldata_final = mycaldata[(mycaldata$locationType %in% input$locationType) & (mycaldata$attendanceType %in% input$attendanceType) & (mycaldata$eventType %in% input$eventType),] 
mycaldata_final = mycaldata[c("calendarId","title","body","recurrenceRule","start","end","category","location","backgroundColor","color","borderColor")]
#toastui::calendar(mycaldata_final, navigation = TRUE, view="month",isReadOnly=TRUE,useDetailPopup = TRUE)
#calendar(mycaldata_final, navigation = TRUE, view="month",isReadOnly=TRUE,useDetailPopup = TRUE) 

```

```{r, echo=FALSE}
toastui::calendar(mycaldata_final, navigation = TRUE, view="month",isReadOnly=TRUE, useDetailPopup = TRUE,height = "1000")
```

::: small
Updated: {{< meta current_date >}} at {{< meta current_time >}} .
:::

<br>

---

<br>

### <span style="color: #2a71d0; font-weight: bold"> **Useful Links**

<br>

Below are links to other sites that includes more information about workshops, social and community events:

- [SAHMRI/SAGC](https://sahmri.org.au/)
- [ABACBS](https://www.abacbs.org/)
- [COMBINE](https://www.combine.org.au/)
- [University of Adelaide](https://www.adelaide.edu.au/)
- [Intersect](https://intersect.org.au/)
- [Galaxy](https://training.galaxyproject.org)
- Slack:
  * [COMBINE](https://combine-au.slack.com/)
  * [Bionformatics Hub/UofA](https://bioinformatics-hub.slack.com/)

For comprehensive resources, including online training, workshops, and recommended books, visit our [Resources](../resources/resources.html) page.

<br>

---

<br>

Can’t find your event on the calendar? Just [reach out](mailto:resources@doppeldata.au), and we’ll make sure to include all the details!

This document is updated regularly to include current social events, workshops & seminars.
